---
title: "Activity 2 - Day 1"
output: github_document
---

```{setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Packages

```{r, load-packages}
library("tidyverse")
library("tidymodels")
library("GGally")
```

## Task3: Load data and

```{r, task-3-load-data-1, message=False, warning=FALSE}
hfi <- readr::read_csv("https://www.openintro.org/data/csv/hfi.csv")
```

```{r, task-3-load-data-2, message=FALSE, warning=FALSE}

hfi %>%
  ggplot(aes(x=hfi$pf_score)) + geom_histogram() + stat_bin(binwidth = 0.5)
```

1.  Is this an observational study or an experiment?
2.  Describe the distribution of `pf_score` Is the distribution skewed? Are there any other interesting/odd features (outliers, multiple peaks, etc.)? What does that tell you about countries' personal freedoms? Is this what you expected to see? Why, or why not?
3.  Excluding `pf_score`, select two other numeric variables (hint: look for `<dbl>` or `<int>` designations) and describe their relationship with each other using an appropriate visualization.

## Task4: Pairwise Selection

```{r task-4-pairwise-selection, warning=FALSE}

hfi %>% 
  select(ends_with("_score")) %>% 
  ggpairs()
```

4\. For each pair of variables, how would you describe the relationship graphically? Do any of the relationships look linear? Are there any interesting/odd features (outliers, non-linear patterns, etc.)?

5\. For each pair of variables, how would you describe the relationship numerically?

## Task 5 Multiple Linear Regression Model

```{r task-5-multiple-linear-regression-model, warning=FALSE}

m_hr_ef <- lm(pf_score ~ hf_score + ef_score, data = hfi)
tidy(m_hr_ef)
```

6\. Using your output, write the complete estimated equation for this model. Remember in Activity 2 that this looked like:

TODO ADD EQUATION HERE

7\. For each of the estimated parameters (the *y*-intercept, and slope associated with each explanatory variable - three total), interpret these values in the context of this problem. That is, what do they mean for a "non-data" person?
